\documentclass{article}\usepackage[eientei, +maths, bbStyle = bbold,margins = minimal, scriptStyle = euler]{kappak}\usepackage{enumitem}\usepackage{multicol}\setlist[enumerate, 1]{noitemsep, nosep}\title{\texttt{kappak} autogenerated documentation}\begin{document}\maketitle\tableofcontents\section{Package options}\begin{multicols}{3}\begin{enumerate}  \item \texttt{alpha}:   \item \texttt{bbStyle}: Sets the mathematical blackboard letter style. Supports \texttt{normal} (default), and \texttt{bbold}.  \item \texttt{bellatrix}:   \item \texttt{bibliographyStyle}: Sets the bibliography style. Only relevant if you use \texttt{kdocument} instead of the standard \texttt{document} environment.  \item \texttt{categoryStyle}: Sets the category style for category theory. Supports \texttt{script} (default), \texttt{bf}, \texttt{rm}, \texttt{sf}, and \texttt{tt}.  \item \texttt{chapterStyle}: Sets the chapter style. Supports \texttt{normal} (default), \texttt{cb}, and \texttt{rb}.  \item \texttt{cortana}:   \item \texttt{durotan}:   \item \texttt{eientei}:   \item \texttt{fontSet}: Sets the font set. Supports \texttt{normal} (default), \texttt{alternate}, and \texttt{xcharter}.  \item \texttt{headerFooterStyle}: Sets the header and footer style. Supports \texttt{normal} (default), \texttt{classic}, \texttt{cb}, and \texttt{empty}.  \item \texttt{language}: Sets the language of the document. Supports \texttt{english} (default), and \texttt{french}.  \item \texttt{lineSpacing}: Sets the line spacing.  \item \texttt{margins}: Sets the margins. Supports \texttt{normal} (default), \texttt{reduced}, and \texttt{minimal}.  \item \texttt{scriptStyle}: Sets the mathematical script style. Supports \texttt{normal} (default), \texttt{euler}, and \texttt{rsfs}.  \item \texttt{titlePageStyle}: Sets the title page style. Supports \texttt{normal} (default), \texttt{classic}, \texttt{bar}, \texttt{gm}, and \texttt{gb}.  \item \texttt{version}: Sets the kappan version to use. Use explicit names instead.\end{enumerate}\end{multicols}\section{Command}\begin{multicols}{3}\begin{enumerate}  \item \texttt{DeclareBigOperator}: Declares a new big operator, akin to \texttt{sum} or \texttt{prod}.  \item \texttt{DeclareRotatedSymbol}: Declares a new symbol that is a rotation of another existing one.  \item \texttt{authorshere}: Inserts the author and the subauthor if it is set. See the \texttt{\\author} and \texttt{\\subauthor} commands.  \item \texttt{coeqdiagram}:   \item \texttt{diagramarrows}: Sets the arrow type for commutative diagrams. Takes 4 arguments among \texttt{->} (default), \texttt{-}, \texttt{<-}, \texttt{<->}, \texttt{->>}, \texttt{<<-}, \texttt{>->}, \texttt{<-<}, \texttt{right hook->}, \texttt{<-left hook}, \texttt{|->}, \texttt{<-|}.  \item \texttt{diagramlines}: Sets the arrow line styles for commutative diagrams. Takes 4 arguments, among \texttt{-} (default), \texttt{=}, \texttt{..}, \texttt{--}.  \item \texttt{diagramsize}:   \item \texttt{editor}: For custome title pages.  \item \texttt{email}: For custome title pages.  \item \texttt{eqdiagram}:   \item \texttt{image}: For custome title pages.  \item \texttt{imagehere}: Inserts the image. See the \texttt{\\image} command.  \item \texttt{kbibliography}: Inserts the bibliography from file \texttt{bibliography.bib}.  \item \texttt{logo}: For custome title pages.  \item \texttt{logohere}: Inserts the logo. See the \texttt{\\logo} command.  \item \texttt{publisher}: For custome title pages.  \item \texttt{pullbackdiagram}: Pullback diagram.  \item \texttt{pushoutdiagram}: Pushout diagram.  \item \texttt{rds}: Resets diagram styles.  \item \texttt{squarediagram}: Square diagram.  \item \texttt{subauthor}: For custome title pages.  \item \texttt{subtitle}: For custome title pages.  \item \texttt{triangleDLdiagram}:   \item \texttt{triangleDRdiagram}:   \item \texttt{triangleDdiagram}:   \item \texttt{triangleLdiagram}:   \item \texttt{triangleRdiagram}:   \item \texttt{triangleULdiagram}:   \item \texttt{triangleURdiagram}:   \item \texttt{triangleUdiagram}: \end{enumerate}\end{multicols}\section{Environments}\begin{multicols}{3}\begin{enumerate}  \item \texttt{dedication}: The \texttt{dedication} environment.  \item \texttt{kdocument}: The \texttt{kdocument} environment.  \item \texttt{proof}: The \texttt{proof} environment.  \item \texttt{proofs}: The \texttt{proofs} environment.  \item \texttt{solution}: The \texttt{solution} environment.  \item \texttt{solutions}: The \texttt{solutions} environment.\end{enumerate}\end{multicols}\section{Theorem environments}\begin{multicols}{3}\begin{enumerate}  \item \texttt{assertion}: The \texttt{assertion} theorem environment.  \item \texttt{assertions}: The \texttt{assertions} theorem environment.  \item \texttt{axiom}: The \texttt{axiom} theorem environment.  \item \texttt{axioms}: The \texttt{axioms} theorem environment.  \item \texttt{conjecture}: The \texttt{conjecture} theorem environment.  \item \texttt{conjectures}: The \texttt{conjectures} theorem environment.  \item \texttt{convention}: The \texttt{convention} theorem environment.  \item \texttt{conventions}: The \texttt{conventions} theorem environment.  \item \texttt{corollaries}: The \texttt{corollaries} theorem environment.  \item \texttt{corollary}: The \texttt{corollary} theorem environment.  \item \texttt{definition}: The \texttt{definition} theorem environment.  \item \texttt{definitions}: The \texttt{definitions} theorem environment.  \item \texttt{example}: The \texttt{example} theorem environment.  \item \texttt{examples}: The \texttt{examples} theorem environment.  \item \texttt{exercise}: The \texttt{exercise} theorem environment.  \item \texttt{exercises}: The \texttt{exercises} theorem environment.  \item \texttt{lemma}: The \texttt{lemma} theorem environment.  \item \texttt{lemmas}: The \texttt{lemmas} theorem environment.  \item \texttt{notation}: The \texttt{notation} theorem environment.  \item \texttt{notations}: The \texttt{notations} theorem environment.  \item \texttt{properties}: The \texttt{properties} theorem environment.  \item \texttt{property}: The \texttt{property} theorem environment.  \item \texttt{proposition}: The \texttt{proposition} theorem environment.  \item \texttt{propositions}: The \texttt{propositions} theorem environment.  \item \texttt{question}: The \texttt{question} theorem environment.  \item \texttt{questions}: The \texttt{questions} theorem environment.  \item \texttt{remark}: The \texttt{remark} theorem environment.  \item \texttt{remarks}: The \texttt{remarks} theorem environment.  \item \texttt{reminder}: The \texttt{reminder} theorem environment.  \item \texttt{reminders}: The \texttt{reminders} theorem environment.  \item \texttt{scholia}: The \texttt{scholia} theorem environment.  \item \texttt{scholias}: The \texttt{scholias} theorem environment.  \item \texttt{terminologies}: The \texttt{terminologies} theorem environment.  \item \texttt{terminology}: The \texttt{terminology} theorem environment.  \item \texttt{theorem}: The \texttt{theorem} theorem environment.  \item \texttt{theorems}: The \texttt{theorems} theorem environment.\end{enumerate}\end{multicols}\section{Mathematics: operators}\begin{multicols}{3}\begin{enumerate}  \item \texttt{Ann}: The $\Ann$ math operator  \item \texttt{Aut}: The $\Aut$ math operator  \item \texttt{Bil}: The $\Bil$ math operator  \item \texttt{Card}: The $\Card$ math operator  \item \texttt{Dom}: The $\Dom$ math operator  \item \texttt{END}: The $\END$ math operator  \item \texttt{End}: The $\End$ math operator  \item \texttt{Ext}: The $\Ext$ math operator  \item \texttt{Frac}: The $\Frac$ math operator  \item \texttt{GL}: The $\GL$ math operator  \item \texttt{Hom}: The $\Hom$ math operator  \item \texttt{Id}: The $\Id$ math operator  \item \texttt{Ind}: The $\Ind$ math operator  \item \texttt{Ker}: The $\Ker$ math operator  \item \texttt{Map}: The $\Map$ math operator  \item \texttt{Mor}: The $\Mor$ math operator  \item \texttt{Ob}: The $\Ob$ math operator  \item \texttt{Orb}: The $\Orb$ math operator  \item \texttt{SL}: The $\SL$ math operator  \item \texttt{Spec}: The $\Spec$ math operator  \item \texttt{Stab}: The $\Stab$ math operator  \item \texttt{Sym}: The $\Sym$ math operator  \item \texttt{Tor}: The $\Tor$ math operator  \item \texttt{car}: The $\car$ math operator  \item \texttt{card}: The $\card$ math operator  \item \texttt{codom}: The $\codom$ math operator  \item \texttt{coker}: The $\coker$ math operator  \item \texttt{colim}: The $\colim$ math operator  \item \texttt{dom}: The $\dom$ math operator  \item \texttt{ev}: The $\ev$ math operator  \item \texttt{id}: The $\id$ math operator  \item \texttt{im}: The $\im$ math operator  \item \texttt{ob}: The $\ob$ math operator  \item \texttt{proj}: The $\proj$ math operator  \item \texttt{rk}: The $\rk$ math operator  \item \texttt{tr}: The $\tr$ math operator\end{enumerate}\end{multicols}\section{Mathematics: category theory}\begin{multicols}{3}\begin{enumerate}  \item \texttt{Ab}: The $\Ab$ category  \item \texttt{Alg}: The $\Alg$ category  \item \texttt{CAT}: The $\CAT$ category  \item \texttt{Cat}: The $\Cat$ category  \item \texttt{Ch}: The $\Ch$ category  \item \texttt{Fin}: The $\Fin$ category  \item \texttt{Graph}: The $\Graph$ category  \item \texttt{Grp}: The $\Grp$ category  \item \texttt{Mod}: The $\Mod$ category  \item \texttt{Mon}: The $\Mon$ category  \item \texttt{Op}: The $\Op$ category  \item \texttt{Pos}: The $\Pos$ category  \item \texttt{Ring}: The $\Ring$ category  \item \texttt{SET}: The $\SET$ category  \item \texttt{Set}: The $\Set$ category  \item \texttt{Sh}: The $\Sh$ category  \item \texttt{Top}: The $\Top$ category  \item \texttt{Vect}: The $\Vect$ category  \item \texttt{catA}: $\catA$.  \item \texttt{catAA}: $\catAA$.  \item \texttt{catB}: $\catB$.  \item \texttt{catBB}: $\catBB$.  \item \texttt{catC}: $\catC$.  \item \texttt{catCC}: $\catCC$.  \item \texttt{catD}: $\catD$.  \item \texttt{catDD}: $\catDD$.  \item \texttt{catE}: $\catE$.  \item \texttt{catEE}: $\catEE$.  \item \texttt{catF}: $\catF$.  \item \texttt{catFF}: $\catFF$.  \item \texttt{catG}: $\catG$.  \item \texttt{catGG}: $\catGG$.  \item \texttt{catH}: $\catH$.  \item \texttt{catHH}: $\catHH$.  \item \texttt{catI}: $\catI$.  \item \texttt{catII}: $\catII$.  \item \texttt{catJ}: $\catJ$.  \item \texttt{catJJ}: $\catJJ$.  \item \texttt{catK}: $\catK$.  \item \texttt{catKK}: $\catKK$.  \item \texttt{catL}: $\catL$.  \item \texttt{catLL}: $\catLL$.  \item \texttt{catM}: $\catM$.  \item \texttt{catMM}: $\catMM$.  \item \texttt{catN}: $\catN$.  \item \texttt{catNN}: $\catNN$.  \item \texttt{catO}: $\catO$.  \item \texttt{catOO}: $\catOO$.  \item \texttt{catP}: $\catP$.  \item \texttt{catPP}: $\catPP$.  \item \texttt{catQ}: $\catQ$.  \item \texttt{catQQ}: $\catQQ$.  \item \texttt{catR}: $\catR$.  \item \texttt{catRR}: $\catRR$.  \item \texttt{catS}: $\catS$.  \item \texttt{catSS}: $\catSS$.  \item \texttt{catT}: $\catT$.  \item \texttt{catTT}: $\catTT$.  \item \texttt{catU}: $\catU$.  \item \texttt{catUU}: $\catUU$.  \item \texttt{catV}: $\catV$.  \item \texttt{catVV}: $\catVV$.  \item \texttt{catW}: $\catW$.  \item \texttt{catWW}: $\catWW$.  \item \texttt{catX}: $\catX$.  \item \texttt{catXX}: $\catXX$.  \item \texttt{catY}: $\catY$.  \item \texttt{catYY}: $\catYY$.  \item \texttt{catZ}: $\catZ$.  \item \texttt{catZZ}: $\catZZ$.  \item \texttt{pSh}: The $\pSh$ category  \item \texttt{sSet}: The $\sSet$ category\end{enumerate}\end{multicols}\section{Mathematics: character styles and accents}\begin{multicols}{3}\begin{enumerate}  \item \texttt{barA}: $\barA$  \item \texttt{barAA}: $\barAA$  \item \texttt{barB}: $\barB$  \item \texttt{barBB}: $\barBB$  \item \texttt{barC}: $\barC$  \item \texttt{barCC}: $\barCC$  \item \texttt{barD}: $\barD$  \item \texttt{barDD}: $\barDD$  \item \texttt{barDelta}: $\barDelta$  \item \texttt{barE}: $\barE$  \item \texttt{barEE}: $\barEE$  \item \texttt{barF}: $\barF$  \item \texttt{barFF}: $\barFF$  \item \texttt{barG}: $\barG$  \item \texttt{barGG}: $\barGG$  \item \texttt{barGamma}: $\barGamma$  \item \texttt{barH}: $\barH$  \item \texttt{barHH}: $\barHH$  \item \texttt{barI}: $\barI$  \item \texttt{barII}: $\barII$  \item \texttt{barJ}: $\barJ$  \item \texttt{barJJ}: $\barJJ$  \item \texttt{barK}: $\barK$  \item \texttt{barKK}: $\barKK$  \item \texttt{barL}: $\barL$  \item \texttt{barLL}: $\barLL$  \item \texttt{barLambda}: $\barLambda$  \item \texttt{barM}: $\barM$  \item \texttt{barMM}: $\barMM$  \item \texttt{barN}: $\barN$  \item \texttt{barNN}: $\barNN$  \item \texttt{barO}: $\barO$  \item \texttt{barOO}: $\barOO$  \item \texttt{barOmega}: $\barOmega$  \item \texttt{barP}: $\barP$  \item \texttt{barPP}: $\barPP$  \item \texttt{barPhi}: $\barPhi$  \item \texttt{barPi}: $\barPi$  \item \texttt{barPsi}: $\barPsi$  \item \texttt{barQ}: $\barQ$  \item \texttt{barQQ}: $\barQQ$  \item \texttt{barR}: $\barR$  \item \texttt{barRR}: $\barRR$  \item \texttt{barS}: $\barS$  \item \texttt{barSS}: $\barSS$  \item \texttt{barSigma}: $\barSigma$  \item \texttt{barT}: $\barT$  \item \texttt{barTT}: $\barTT$  \item \texttt{barTheta}: $\barTheta$  \item \texttt{barU}: $\barU$  \item \texttt{barUU}: $\barUU$  \item \texttt{barUpsilon}: $\barUpsilon$  \item \texttt{barV}: $\barV$  \item \texttt{barVV}: $\barVV$  \item \texttt{barW}: $\barW$  \item \texttt{barWW}: $\barWW$  \item \texttt{barX}: $\barX$  \item \texttt{barXX}: $\barXX$  \item \texttt{barXi}: $\barXi$  \item \texttt{barY}: $\barY$  \item \texttt{barYY}: $\barYY$  \item \texttt{barZ}: $\barZ$  \item \texttt{barZZ}: $\barZZ$  \item \texttt{baralpha}: $\baralpha$  \item \texttt{barbeta}: $\barbeta$  \item \texttt{barchi}: $\barchi$  \item \texttt{bardelta}: $\bardelta$  \item \texttt{barepsilon}: $\barepsilon$  \item \texttt{bareta}: $\bareta$  \item \texttt{bargamma}: $\bargamma$  \item \texttt{bariota}: $\bariota$  \item \texttt{barkappa}: $\barkappa$  \item \texttt{barlambda}: $\barlambda$  \item \texttt{barmu}: $\barmu$  \item \texttt{barnu}: $\barnu$  \item \texttt{baromega}: $\baromega$  \item \texttt{barphi}: $\barphi$  \item \texttt{barpi}: $\barpi$  \item \texttt{barpsi}: $\barpsi$  \item \texttt{barrho}: $\barrho$  \item \texttt{barsigma}: $\barsigma$  \item \texttt{bartau}: $\bartau$  \item \texttt{bartheta}: $\bartheta$  \item \texttt{barupsilon}: $\barupsilon$  \item \texttt{barvarepsilon}: $\barvarepsilon$  \item \texttt{barvarphi}: $\barvarphi$  \item \texttt{barvarpi}: $\barvarpi$  \item \texttt{barvarrho}: $\barvarrho$  \item \texttt{barvarsigma}: $\barvarsigma$  \item \texttt{barvartheta}: $\barvartheta$  \item \texttt{barxi}: $\barxi$  \item \texttt{barzeta}: $\barzeta$  \item \texttt{bbA}: $\bbA$  \item \texttt{bbAA}: $\bbAA$  \item \texttt{bbB}: $\bbB$  \item \texttt{bbBB}: $\bbBB$  \item \texttt{bbC}: $\bbC$  \item \texttt{bbCC}: $\bbCC$  \item \texttt{bbD}: $\bbD$  \item \texttt{bbDD}: $\bbDD$  \item \texttt{bbDelta}: $\bbDelta$  \item \texttt{bbE}: $\bbE$  \item \texttt{bbEE}: $\bbEE$  \item \texttt{bbF}: $\bbF$  \item \texttt{bbFF}: $\bbFF$  \item \texttt{bbG}: $\bbG$  \item \texttt{bbGG}: $\bbGG$  \item \texttt{bbGamma}: $\bbGamma$  \item \texttt{bbH}: $\bbH$  \item \texttt{bbHH}: $\bbHH$  \item \texttt{bbI}: $\bbI$  \item \texttt{bbII}: $\bbII$  \item \texttt{bbJ}: $\bbJ$  \item \texttt{bbJJ}: $\bbJJ$  \item \texttt{bbK}: $\bbK$  \item \texttt{bbK}: $\bbK$  \item \texttt{bbKK}: $\bbKK$  \item \texttt{bbL}: $\bbL$  \item \texttt{bbLL}: $\bbLL$  \item \texttt{bbLambda}: $\bbLambda$  \item \texttt{bbM}: $\bbM$  \item \texttt{bbMM}: $\bbMM$  \item \texttt{bbN}: $\bbN$  \item \texttt{bbNN}: $\bbNN$  \item \texttt{bbO}: $\bbO$  \item \texttt{bbOO}: $\bbOO$  \item \texttt{bbOmega}: $\bbOmega$  \item \texttt{bbP}: $\bbP$  \item \texttt{bbPP}: $\bbPP$  \item \texttt{bbPhi}: $\bbPhi$  \item \texttt{bbPi}: $\bbPi$  \item \texttt{bbPsi}: $\bbPsi$  \item \texttt{bbQ}: $\bbQ$  \item \texttt{bbQQ}: $\bbQQ$  \item \texttt{bbR}: $\bbR$  \item \texttt{bbRR}: $\bbRR$  \item \texttt{bbS}: $\bbS$  \item \texttt{bbSS}: $\bbSS$  \item \texttt{bbSigma}: $\bbSigma$  \item \texttt{bbT}: $\bbT$  \item \texttt{bbTT}: $\bbTT$  \item \texttt{bbTheta}: $\bbTheta$  \item \texttt{bbU}: $\bbU$  \item \texttt{bbUU}: $\bbUU$  \item \texttt{bbUpsilon}: $\bbUpsilon$  \item \texttt{bbV}: $\bbV$  \item \texttt{bbVV}: $\bbVV$  \item \texttt{bbW}: $\bbW$  \item \texttt{bbWW}: $\bbWW$  \item \texttt{bbX}: $\bbX$  \item \texttt{bbXX}: $\bbXX$  \item \texttt{bbXi}: $\bbXi$  \item \texttt{bbY}: $\bbY$  \item \texttt{bbYY}: $\bbYY$  \item \texttt{bbZ}: $\bbZ$  \item \texttt{bbZZ}: $\bbZZ$  \item \texttt{bbalpha}: $\bbalpha$  \item \texttt{bbarA}: $\bbarA$  \item \texttt{bbarAA}: $\bbarAA$  \item \texttt{bbarB}: $\bbarB$  \item \texttt{bbarBB}: $\bbarBB$  \item \texttt{bbarC}: $\bbarC$  \item \texttt{bbarCC}: $\bbarCC$  \item \texttt{bbarD}: $\bbarD$  \item \texttt{bbarDD}: $\bbarDD$  \item \texttt{bbarDelta}: $\bbarDelta$  \item \texttt{bbarE}: $\bbarE$  \item \texttt{bbarEE}: $\bbarEE$  \item \texttt{bbarF}: $\bbarF$  \item \texttt{bbarFF}: $\bbarFF$  \item \texttt{bbarG}: $\bbarG$  \item \texttt{bbarGG}: $\bbarGG$  \item \texttt{bbarGamma}: $\bbarGamma$  \item \texttt{bbarH}: $\bbarH$  \item \texttt{bbarHH}: $\bbarHH$  \item \texttt{bbarI}: $\bbarI$  \item \texttt{bbarII}: $\bbarII$  \item \texttt{bbarJ}: $\bbarJ$  \item \texttt{bbarJJ}: $\bbarJJ$  \item \texttt{bbarK}: $\bbarK$  \item \texttt{bbarKK}: $\bbarKK$  \item \texttt{bbarL}: $\bbarL$  \item \texttt{bbarLL}: $\bbarLL$  \item \texttt{bbarLambda}: $\bbarLambda$  \item \texttt{bbarM}: $\bbarM$  \item \texttt{bbarMM}: $\bbarMM$  \item \texttt{bbarN}: $\bbarN$  \item \texttt{bbarNN}: $\bbarNN$  \item \texttt{bbarO}: $\bbarO$  \item \texttt{bbarOO}: $\bbarOO$  \item \texttt{bbarOmega}: $\bbarOmega$  \item \texttt{bbarP}: $\bbarP$  \item \texttt{bbarPP}: $\bbarPP$  \item \texttt{bbarPhi}: $\bbarPhi$  \item \texttt{bbarPi}: $\bbarPi$  \item \texttt{bbarPsi}: $\bbarPsi$  \item \texttt{bbarQ}: $\bbarQ$  \item \texttt{bbarQQ}: $\bbarQQ$  \item \texttt{bbarR}: $\bbarR$  \item \texttt{bbarRR}: $\bbarRR$  \item \texttt{bbarS}: $\bbarS$  \item \texttt{bbarSS}: $\bbarSS$  \item \texttt{bbarSigma}: $\bbarSigma$  \item \texttt{bbarT}: $\bbarT$  \item \texttt{bbarTT}: $\bbarTT$  \item \texttt{bbarTheta}: $\bbarTheta$  \item \texttt{bbarU}: $\bbarU$  \item \texttt{bbarUU}: $\bbarUU$  \item \texttt{bbarUpsilon}: $\bbarUpsilon$  \item \texttt{bbarV}: $\bbarV$  \item \texttt{bbarVV}: $\bbarVV$  \item \texttt{bbarW}: $\bbarW$  \item \texttt{bbarWW}: $\bbarWW$  \item \texttt{bbarX}: $\bbarX$  \item \texttt{bbarXX}: $\bbarXX$  \item \texttt{bbarXi}: $\bbarXi$  \item \texttt{bbarY}: $\bbarY$  \item \texttt{bbarYY}: $\bbarYY$  \item \texttt{bbarZ}: $\bbarZ$  \item \texttt{bbarZZ}: $\bbarZZ$  \item \texttt{bbaralpha}: $\bbaralpha$  \item \texttt{bbarbeta}: $\bbarbeta$  \item \texttt{bbarchi}: $\bbarchi$  \item \texttt{bbardelta}: $\bbardelta$  \item \texttt{bbarepsilon}: $\bbarepsilon$  \item \texttt{bbareta}: $\bbareta$  \item \texttt{bbargamma}: $\bbargamma$  \item \texttt{bbariota}: $\bbariota$  \item \texttt{bbarkappa}: $\bbarkappa$  \item \texttt{bbarlambda}: $\bbarlambda$  \item \texttt{bbarmu}: $\bbarmu$  \item \texttt{bbarnu}: $\bbarnu$  \item \texttt{bbaromega}: $\bbaromega$  \item \texttt{bbarphi}: $\bbarphi$  \item \texttt{bbarpi}: $\bbarpi$  \item \texttt{bbarpsi}: $\bbarpsi$  \item \texttt{bbarrho}: $\bbarrho$  \item \texttt{bbarsigma}: $\bbarsigma$  \item \texttt{bbartau}: $\bbartau$  \item \texttt{bbartheta}: $\bbartheta$  \item \texttt{bbarupsilon}: $\bbarupsilon$  \item \texttt{bbarvarepsilon}: $\bbarvarepsilon$  \item \texttt{bbarvarphi}: $\bbarvarphi$  \item \texttt{bbarvarpi}: $\bbarvarpi$  \item \texttt{bbarvarrho}: $\bbarvarrho$  \item \texttt{bbarvarsigma}: $\bbarvarsigma$  \item \texttt{bbarvartheta}: $\bbarvartheta$  \item \texttt{bbarxi}: $\bbarxi$  \item \texttt{bbarzeta}: $\bbarzeta$  \item \texttt{bbbeta}: $\bbbeta$  \item \texttt{bbchi}: $\bbchi$  \item \texttt{bbdelta}: $\bbdelta$  \item \texttt{bbepsilon}: $\bbepsilon$  \item \texttt{bbeta}: $\bbeta$  \item \texttt{bbgamma}: $\bbgamma$  \item \texttt{bbiota}: $\bbiota$  \item \texttt{bbkappa}: $\bbkappa$  \item \texttt{bblambda}: $\bblambda$  \item \texttt{bbmu}: $\bbmu$  \item \texttt{bbnu}: $\bbnu$  \item \texttt{bbomega}: $\bbomega$  \item \texttt{bbphi}: $\bbphi$  \item \texttt{bbpi}: $\bbpi$  \item \texttt{bbpsi}: $\bbpsi$  \item \texttt{bbrho}: $\bbrho$  \item \texttt{bbsigma}: $\bbsigma$  \item \texttt{bbtau}: $\bbtau$  \item \texttt{bbtheta}: $\bbtheta$  \item \texttt{bbupsilon}: $\bbupsilon$  \item \texttt{bbvarepsilon}: $\bbvarepsilon$  \item \texttt{bbvarphi}: $\bbvarphi$  \item \texttt{bbvarpi}: $\bbvarpi$  \item \texttt{bbvarrho}: $\bbvarrho$  \item \texttt{bbvarsigma}: $\bbvarsigma$  \item \texttt{bbvartheta}: $\bbvartheta$  \item \texttt{bbxi}: $\bbxi$  \item \texttt{bbzeta}: $\bbzeta$  \item \texttt{bfA}: $\bfA$  \item \texttt{bfAA}: $\bfAA$  \item \texttt{bfB}: $\bfB$  \item \texttt{bfBB}: $\bfBB$  \item \texttt{bfC}: $\bfC$  \item \texttt{bfCC}: $\bfCC$  \item \texttt{bfD}: $\bfD$  \item \texttt{bfDD}: $\bfDD$  \item \texttt{bfDelta}: $\bfDelta$  \item \texttt{bfE}: $\bfE$  \item \texttt{bfEE}: $\bfEE$  \item \texttt{bfF}: $\bfF$  \item \texttt{bfFF}: $\bfFF$  \item \texttt{bfG}: $\bfG$  \item \texttt{bfGG}: $\bfGG$  \item \texttt{bfGamma}: $\bfGamma$  \item \texttt{bfH}: $\bfH$  \item \texttt{bfHH}: $\bfHH$  \item \texttt{bfI}: $\bfI$  \item \texttt{bfII}: $\bfII$  \item \texttt{bfJ}: $\bfJ$  \item \texttt{bfJJ}: $\bfJJ$  \item \texttt{bfK}: $\bfK$  \item \texttt{bfKK}: $\bfKK$  \item \texttt{bfL}: $\bfL$  \item \texttt{bfLL}: $\bfLL$  \item \texttt{bfLambda}: $\bfLambda$  \item \texttt{bfM}: $\bfM$  \item \texttt{bfMM}: $\bfMM$  \item \texttt{bfN}: $\bfN$  \item \texttt{bfNN}: $\bfNN$  \item \texttt{bfO}: $\bfO$  \item \texttt{bfOO}: $\bfOO$  \item \texttt{bfOmega}: $\bfOmega$  \item \texttt{bfP}: $\bfP$  \item \texttt{bfPP}: $\bfPP$  \item \texttt{bfPhi}: $\bfPhi$  \item \texttt{bfPi}: $\bfPi$  \item \texttt{bfPsi}: $\bfPsi$  \item \texttt{bfQ}: $\bfQ$  \item \texttt{bfQQ}: $\bfQQ$  \item \texttt{bfR}: $\bfR$  \item \texttt{bfRR}: $\bfRR$  \item \texttt{bfS}: $\bfS$  \item \texttt{bfSS}: $\bfSS$  \item \texttt{bfSigma}: $\bfSigma$  \item \texttt{bfT}: $\bfT$  \item \texttt{bfTT}: $\bfTT$  \item \texttt{bfTheta}: $\bfTheta$  \item \texttt{bfU}: $\bfU$  \item \texttt{bfUU}: $\bfUU$  \item \texttt{bfUpsilon}: $\bfUpsilon$  \item \texttt{bfV}: $\bfV$  \item \texttt{bfVV}: $\bfVV$  \item \texttt{bfW}: $\bfW$  \item \texttt{bfWW}: $\bfWW$  \item \texttt{bfX}: $\bfX$  \item \texttt{bfXX}: $\bfXX$  \item \texttt{bfXi}: $\bfXi$  \item \texttt{bfY}: $\bfY$  \item \texttt{bfYY}: $\bfYY$  \item \texttt{bfZ}: $\bfZ$  \item \texttt{bfZZ}: $\bfZZ$  \item \texttt{bfalpha}: $\bfalpha$  \item \texttt{bfbeta}: $\bfbeta$  \item \texttt{bfchi}: $\bfchi$  \item \texttt{bfdelta}: $\bfdelta$  \item \texttt{bfepsilon}: $\bfepsilon$  \item \texttt{bfeta}: $\bfeta$  \item \texttt{bfgamma}: $\bfgamma$  \item \texttt{bfiota}: $\bfiota$  \item \texttt{bfkappa}: $\bfkappa$  \item \texttt{bflambda}: $\bflambda$  \item \texttt{bfmu}: $\bfmu$  \item \texttt{bfnu}: $\bfnu$  \item \texttt{bfomega}: $\bfomega$  \item \texttt{bfphi}: $\bfphi$  \item \texttt{bfpi}: $\bfpi$  \item \texttt{bfpsi}: $\bfpsi$  \item \texttt{bfrho}: $\bfrho$  \item \texttt{bfsigma}: $\bfsigma$  \item \texttt{bftau}: $\bftau$  \item \texttt{bftheta}: $\bftheta$  \item \texttt{bfupsilon}: $\bfupsilon$  \item \texttt{bfvarepsilon}: $\bfvarepsilon$  \item \texttt{bfvarphi}: $\bfvarphi$  \item \texttt{bfvarpi}: $\bfvarpi$  \item \texttt{bfvarrho}: $\bfvarrho$  \item \texttt{bfvarsigma}: $\bfvarsigma$  \item \texttt{bfvartheta}: $\bfvartheta$  \item \texttt{bfxi}: $\bfxi$  \item \texttt{bfzeta}: $\bfzeta$  \item \texttt{calA}: $\calA$  \item \texttt{calAA}: $\calAA$  \item \texttt{calB}: $\calB$  \item \texttt{calBB}: $\calBB$  \item \texttt{calC}: $\calC$  \item \texttt{calCC}: $\calCC$  \item \texttt{calD}: $\calD$  \item \texttt{calDD}: $\calDD$  \item \texttt{calE}: $\calE$  \item \texttt{calEE}: $\calEE$  \item \texttt{calF}: $\calF$  \item \texttt{calFF}: $\calFF$  \item \texttt{calG}: $\calG$  \item \texttt{calGG}: $\calGG$  \item \texttt{calH}: $\calH$  \item \texttt{calHH}: $\calHH$  \item \texttt{calI}: $\calI$  \item \texttt{calII}: $\calII$  \item \texttt{calJ}: $\calJ$  \item \texttt{calJJ}: $\calJJ$  \item \texttt{calK}: $\calK$  \item \texttt{calKK}: $\calKK$  \item \texttt{calL}: $\calL$  \item \texttt{calLL}: $\calLL$  \item \texttt{calM}: $\calM$  \item \texttt{calMM}: $\calMM$  \item \texttt{calN}: $\calN$  \item \texttt{calNN}: $\calNN$  \item \texttt{calO}: $\calO$  \item \texttt{calOO}: $\calOO$  \item \texttt{calP}: $\calP$  \item \texttt{calPP}: $\calPP$  \item \texttt{calQ}: $\calQ$  \item \texttt{calQQ}: $\calQQ$  \item \texttt{calR}: $\calR$  \item \texttt{calRR}: $\calRR$  \item \texttt{calS}: $\calS$  \item \texttt{calSS}: $\calSS$  \item \texttt{calT}: $\calT$  \item \texttt{calTT}: $\calTT$  \item \texttt{calU}: $\calU$  \item \texttt{calUU}: $\calUU$  \item \texttt{calV}: $\calV$  \item \texttt{calVV}: $\calVV$  \item \texttt{calW}: $\calW$  \item \texttt{calWW}: $\calWW$  \item \texttt{calX}: $\calX$  \item \texttt{calXX}: $\calXX$  \item \texttt{calY}: $\calY$  \item \texttt{calYY}: $\calYY$  \item \texttt{calZ}: $\calZ$  \item \texttt{calZZ}: $\calZZ$  \item \texttt{chA}: $\chA$  \item \texttt{chAA}: $\chAA$  \item \texttt{chB}: $\chB$  \item \texttt{chBB}: $\chBB$  \item \texttt{chC}: $\chC$  \item \texttt{chCC}: $\chCC$  \item \texttt{chD}: $\chD$  \item \texttt{chDD}: $\chDD$  \item \texttt{chDelta}: $\chDelta$  \item \texttt{chE}: $\chE$  \item \texttt{chEE}: $\chEE$  \item \texttt{chF}: $\chF$  \item \texttt{chFF}: $\chFF$  \item \texttt{chG}: $\chG$  \item \texttt{chGG}: $\chGG$  \item \texttt{chGamma}: $\chGamma$  \item \texttt{chH}: $\chH$  \item \texttt{chHH}: $\chHH$  \item \texttt{chI}: $\chI$  \item \texttt{chII}: $\chII$  \item \texttt{chJ}: $\chJ$  \item \texttt{chJJ}: $\chJJ$  \item \texttt{chK}: $\chK$  \item \texttt{chKK}: $\chKK$  \item \texttt{chL}: $\chL$  \item \texttt{chLL}: $\chLL$  \item \texttt{chLambda}: $\chLambda$  \item \texttt{chM}: $\chM$  \item \texttt{chMM}: $\chMM$  \item \texttt{chN}: $\chN$  \item \texttt{chNN}: $\chNN$  \item \texttt{chO}: $\chO$  \item \texttt{chOO}: $\chOO$  \item \texttt{chOmega}: $\chOmega$  \item \texttt{chP}: $\chP$  \item \texttt{chPP}: $\chPP$  \item \texttt{chPhi}: $\chPhi$  \item \texttt{chPi}: $\chPi$  \item \texttt{chPsi}: $\chPsi$  \item \texttt{chQ}: $\chQ$  \item \texttt{chQQ}: $\chQQ$  \item \texttt{chR}: $\chR$  \item \texttt{chRR}: $\chRR$  \item \texttt{chS}: $\chS$  \item \texttt{chSS}: $\chSS$  \item \texttt{chSigma}: $\chSigma$  \item \texttt{chT}: $\chT$  \item \texttt{chTT}: $\chTT$  \item \texttt{chTheta}: $\chTheta$  \item \texttt{chU}: $\chU$  \item \texttt{chUU}: $\chUU$  \item \texttt{chUpsilon}: $\chUpsilon$  \item \texttt{chV}: $\chV$  \item \texttt{chVV}: $\chVV$  \item \texttt{chW}: $\chW$  \item \texttt{chWW}: $\chWW$  \item \texttt{chX}: $\chX$  \item \texttt{chXX}: $\chXX$  \item \texttt{chXi}: $\chXi$  \item \texttt{chY}: $\chY$  \item \texttt{chYY}: $\chYY$  \item \texttt{chZ}: $\chZ$  \item \texttt{chZZ}: $\chZZ$  \item \texttt{chalpha}: $\chalpha$  \item \texttt{chbeta}: $\chbeta$  \item \texttt{chchi}: $\chchi$  \item \texttt{chdelta}: $\chdelta$  \item \texttt{chepsilon}: $\chepsilon$  \item \texttt{cheta}: $\cheta$  \item \texttt{chgamma}: $\chgamma$  \item \texttt{chiota}: $\chiota$  \item \texttt{chkappa}: $\chkappa$  \item \texttt{chlambda}: $\chlambda$  \item \texttt{chmu}: $\chmu$  \item \texttt{chnu}: $\chnu$  \item \texttt{chomega}: $\chomega$  \item \texttt{chphi}: $\chphi$  \item \texttt{chpi}: $\chpi$  \item \texttt{chpsi}: $\chpsi$  \item \texttt{chrho}: $\chrho$  \item \texttt{chsigma}: $\chsigma$  \item \texttt{chtau}: $\chtau$  \item \texttt{chtheta}: $\chtheta$  \item \texttt{chupsilon}: $\chupsilon$  \item \texttt{chvarepsilon}: $\chvarepsilon$  \item \texttt{chvarphi}: $\chvarphi$  \item \texttt{chvarpi}: $\chvarpi$  \item \texttt{chvarrho}: $\chvarrho$  \item \texttt{chvarsigma}: $\chvarsigma$  \item \texttt{chvartheta}: $\chvartheta$  \item \texttt{chxi}: $\chxi$  \item \texttt{chzeta}: $\chzeta$  \item \texttt{ddotA}: $\ddotA$  \item \texttt{ddotAA}: $\ddotAA$  \item \texttt{ddotB}: $\ddotB$  \item \texttt{ddotBB}: $\ddotBB$  \item \texttt{ddotC}: $\ddotC$  \item \texttt{ddotCC}: $\ddotCC$  \item \texttt{ddotD}: $\ddotD$  \item \texttt{ddotDD}: $\ddotDD$  \item \texttt{ddotDelta}: $\ddotDelta$  \item \texttt{ddotE}: $\ddotE$  \item \texttt{ddotEE}: $\ddotEE$  \item \texttt{ddotF}: $\ddotF$  \item \texttt{ddotFF}: $\ddotFF$  \item \texttt{ddotG}: $\ddotG$  \item \texttt{ddotGG}: $\ddotGG$  \item \texttt{ddotGamma}: $\ddotGamma$  \item \texttt{ddotH}: $\ddotH$  \item \texttt{ddotHH}: $\ddotHH$  \item \texttt{ddotI}: $\ddotI$  \item \texttt{ddotII}: $\ddotII$  \item \texttt{ddotJ}: $\ddotJ$  \item \texttt{ddotJJ}: $\ddotJJ$  \item \texttt{ddotK}: $\ddotK$  \item \texttt{ddotKK}: $\ddotKK$  \item \texttt{ddotL}: $\ddotL$  \item \texttt{ddotLL}: $\ddotLL$  \item \texttt{ddotLambda}: $\ddotLambda$  \item \texttt{ddotM}: $\ddotM$  \item \texttt{ddotMM}: $\ddotMM$  \item \texttt{ddotN}: $\ddotN$  \item \texttt{ddotNN}: $\ddotNN$  \item \texttt{ddotO}: $\ddotO$  \item \texttt{ddotOO}: $\ddotOO$  \item \texttt{ddotOmega}: $\ddotOmega$  \item \texttt{ddotP}: $\ddotP$  \item \texttt{ddotPP}: $\ddotPP$  \item \texttt{ddotPhi}: $\ddotPhi$  \item \texttt{ddotPi}: $\ddotPi$  \item \texttt{ddotPsi}: $\ddotPsi$  \item \texttt{ddotQ}: $\ddotQ$  \item \texttt{ddotQQ}: $\ddotQQ$  \item \texttt{ddotR}: $\ddotR$  \item \texttt{ddotRR}: $\ddotRR$  \item \texttt{ddotS}: $\ddotS$  \item \texttt{ddotSS}: $\ddotSS$  \item \texttt{ddotSigma}: $\ddotSigma$  \item \texttt{ddotT}: $\ddotT$  \item \texttt{ddotTT}: $\ddotTT$  \item \texttt{ddotTheta}: $\ddotTheta$  \item \texttt{ddotU}: $\ddotU$  \item \texttt{ddotUU}: $\ddotUU$  \item \texttt{ddotUpsilon}: $\ddotUpsilon$  \item \texttt{ddotV}: $\ddotV$  \item \texttt{ddotVV}: $\ddotVV$  \item \texttt{ddotW}: $\ddotW$  \item \texttt{ddotWW}: $\ddotWW$  \item \texttt{ddotX}: $\ddotX$  \item \texttt{ddotXX}: $\ddotXX$  \item \texttt{ddotXi}: $\ddotXi$  \item \texttt{ddotY}: $\ddotY$  \item \texttt{ddotYY}: $\ddotYY$  \item \texttt{ddotZ}: $\ddotZ$  \item \texttt{ddotZZ}: $\ddotZZ$  \item \texttt{ddotalpha}: $\ddotalpha$  \item \texttt{ddotbeta}: $\ddotbeta$  \item \texttt{ddotchi}: $\ddotchi$  \item \texttt{ddotdelta}: $\ddotdelta$  \item \texttt{ddotepsilon}: $\ddotepsilon$  \item \texttt{ddoteta}: $\ddoteta$  \item \texttt{ddotgamma}: $\ddotgamma$  \item \texttt{ddotiota}: $\ddotiota$  \item \texttt{ddotkappa}: $\ddotkappa$  \item \texttt{ddotlambda}: $\ddotlambda$  \item \texttt{ddotmu}: $\ddotmu$  \item \texttt{ddotnu}: $\ddotnu$  \item \texttt{ddotomega}: $\ddotomega$  \item \texttt{ddotphi}: $\ddotphi$  \item \texttt{ddotpi}: $\ddotpi$  \item \texttt{ddotpsi}: $\ddotpsi$  \item \texttt{ddotrho}: $\ddotrho$  \item \texttt{ddotsigma}: $\ddotsigma$  \item \texttt{ddottau}: $\ddottau$  \item \texttt{ddottheta}: $\ddottheta$  \item \texttt{ddotupsilon}: $\ddotupsilon$  \item \texttt{ddotvarepsilon}: $\ddotvarepsilon$  \item \texttt{ddotvarphi}: $\ddotvarphi$  \item \texttt{ddotvarpi}: $\ddotvarpi$  \item \texttt{ddotvarrho}: $\ddotvarrho$  \item \texttt{ddotvarsigma}: $\ddotvarsigma$  \item \texttt{ddotvartheta}: $\ddotvartheta$  \item \texttt{ddotxi}: $\ddotxi$  \item \texttt{ddotzeta}: $\ddotzeta$  \item \texttt{dotA}: $\dotA$  \item \texttt{dotAA}: $\dotAA$  \item \texttt{dotB}: $\dotB$  \item \texttt{dotBB}: $\dotBB$  \item \texttt{dotC}: $\dotC$  \item \texttt{dotCC}: $\dotCC$  \item \texttt{dotD}: $\dotD$  \item \texttt{dotDD}: $\dotDD$  \item \texttt{dotDelta}: $\dotDelta$  \item \texttt{dotE}: $\dotE$  \item \texttt{dotEE}: $\dotEE$  \item \texttt{dotF}: $\dotF$  \item \texttt{dotFF}: $\dotFF$  \item \texttt{dotG}: $\dotG$  \item \texttt{dotGG}: $\dotGG$  \item \texttt{dotGamma}: $\dotGamma$  \item \texttt{dotH}: $\dotH$  \item \texttt{dotHH}: $\dotHH$  \item \texttt{dotI}: $\dotI$  \item \texttt{dotII}: $\dotII$  \item \texttt{dotJ}: $\dotJ$  \item \texttt{dotJJ}: $\dotJJ$  \item \texttt{dotK}: $\dotK$  \item \texttt{dotKK}: $\dotKK$  \item \texttt{dotL}: $\dotL$  \item \texttt{dotLL}: $\dotLL$  \item \texttt{dotLambda}: $\dotLambda$  \item \texttt{dotM}: $\dotM$  \item \texttt{dotMM}: $\dotMM$  \item \texttt{dotN}: $\dotN$  \item \texttt{dotNN}: $\dotNN$  \item \texttt{dotO}: $\dotO$  \item \texttt{dotOO}: $\dotOO$  \item \texttt{dotOmega}: $\dotOmega$  \item \texttt{dotP}: $\dotP$  \item \texttt{dotPP}: $\dotPP$  \item \texttt{dotPhi}: $\dotPhi$  \item \texttt{dotPi}: $\dotPi$  \item \texttt{dotPsi}: $\dotPsi$  \item \texttt{dotQ}: $\dotQ$  \item \texttt{dotQQ}: $\dotQQ$  \item \texttt{dotR}: $\dotR$  \item \texttt{dotRR}: $\dotRR$  \item \texttt{dotS}: $\dotS$  \item \texttt{dotSS}: $\dotSS$  \item \texttt{dotSigma}: $\dotSigma$  \item \texttt{dotT}: $\dotT$  \item \texttt{dotTT}: $\dotTT$  \item \texttt{dotTheta}: $\dotTheta$  \item \texttt{dotU}: $\dotU$  \item \texttt{dotUU}: $\dotUU$  \item \texttt{dotUpsilon}: $\dotUpsilon$  \item \texttt{dotV}: $\dotV$  \item \texttt{dotVV}: $\dotVV$  \item \texttt{dotW}: $\dotW$  \item \texttt{dotWW}: $\dotWW$  \item \texttt{dotX}: $\dotX$  \item \texttt{dotXX}: $\dotXX$  \item \texttt{dotXi}: $\dotXi$  \item \texttt{dotY}: $\dotY$  \item \texttt{dotYY}: $\dotYY$  \item \texttt{dotZ}: $\dotZ$  \item \texttt{dotZZ}: $\dotZZ$  \item \texttt{dotalpha}: $\dotalpha$  \item \texttt{dotbeta}: $\dotbeta$  \item \texttt{dotchi}: $\dotchi$  \item \texttt{dotdelta}: $\dotdelta$  \item \texttt{dotepsilon}: $\dotepsilon$  \item \texttt{doteta}: $\doteta$  \item \texttt{dotgamma}: $\dotgamma$  \item \texttt{dotiota}: $\dotiota$  \item \texttt{dotkappa}: $\dotkappa$  \item \texttt{dotlambda}: $\dotlambda$  \item \texttt{dotmu}: $\dotmu$  \item \texttt{dotnu}: $\dotnu$  \item \texttt{dotomega}: $\dotomega$  \item \texttt{dotphi}: $\dotphi$  \item \texttt{dotpi}: $\dotpi$  \item \texttt{dotpsi}: $\dotpsi$  \item \texttt{dotrho}: $\dotrho$  \item \texttt{dotsigma}: $\dotsigma$  \item \texttt{dottau}: $\dottau$  \item \texttt{dottheta}: $\dottheta$  \item \texttt{dotupsilon}: $\dotupsilon$  \item \texttt{dotvarepsilon}: $\dotvarepsilon$  \item \texttt{dotvarphi}: $\dotvarphi$  \item \texttt{dotvarpi}: $\dotvarpi$  \item \texttt{dotvarrho}: $\dotvarrho$  \item \texttt{dotvarsigma}: $\dotvarsigma$  \item \texttt{dotvartheta}: $\dotvartheta$  \item \texttt{dotxi}: $\dotxi$  \item \texttt{dotzeta}: $\dotzeta$  \item \texttt{frakA}: $\frakA$  \item \texttt{frakAA}: $\frakAA$  \item \texttt{frakB}: $\frakB$  \item \texttt{frakBB}: $\frakBB$  \item \texttt{frakC}: $\frakC$  \item \texttt{frakCC}: $\frakCC$  \item \texttt{frakD}: $\frakD$  \item \texttt{frakDD}: $\frakDD$  \item \texttt{frakE}: $\frakE$  \item \texttt{frakEE}: $\frakEE$  \item \texttt{frakF}: $\frakF$  \item \texttt{frakFF}: $\frakFF$  \item \texttt{frakG}: $\frakG$  \item \texttt{frakGG}: $\frakGG$  \item \texttt{frakH}: $\frakH$  \item \texttt{frakHH}: $\frakHH$  \item \texttt{frakI}: $\frakI$  \item \texttt{frakII}: $\frakII$  \item \texttt{frakJ}: $\frakJ$  \item \texttt{frakJJ}: $\frakJJ$  \item \texttt{frakK}: $\frakK$  \item \texttt{frakKK}: $\frakKK$  \item \texttt{frakL}: $\frakL$  \item \texttt{frakLL}: $\frakLL$  \item \texttt{frakM}: $\frakM$  \item \texttt{frakMM}: $\frakMM$  \item \texttt{frakN}: $\frakN$  \item \texttt{frakNN}: $\frakNN$  \item \texttt{frakO}: $\frakO$  \item \texttt{frakOO}: $\frakOO$  \item \texttt{frakP}: $\frakP$  \item \texttt{frakPP}: $\frakPP$  \item \texttt{frakQ}: $\frakQ$  \item \texttt{frakQQ}: $\frakQQ$  \item \texttt{frakR}: $\frakR$  \item \texttt{frakRR}: $\frakRR$  \item \texttt{frakS}: $\frakS$  \item \texttt{frakSS}: $\frakSS$  \item \texttt{frakT}: $\frakT$  \item \texttt{frakTT}: $\frakTT$  \item \texttt{frakU}: $\frakU$  \item \texttt{frakUU}: $\frakUU$  \item \texttt{frakV}: $\frakV$  \item \texttt{frakVV}: $\frakVV$  \item \texttt{frakW}: $\frakW$  \item \texttt{frakWW}: $\frakWW$  \item \texttt{frakX}: $\frakX$  \item \texttt{frakXX}: $\frakXX$  \item \texttt{frakY}: $\frakY$  \item \texttt{frakYY}: $\frakYY$  \item \texttt{frakZ}: $\frakZ$  \item \texttt{frakZZ}: $\frakZZ$  \item \texttt{hatA}: $\hatA$  \item \texttt{hatAA}: $\hatAA$  \item \texttt{hatB}: $\hatB$  \item \texttt{hatBB}: $\hatBB$  \item \texttt{hatC}: $\hatC$  \item \texttt{hatCC}: $\hatCC$  \item \texttt{hatD}: $\hatD$  \item \texttt{hatDD}: $\hatDD$  \item \texttt{hatDelta}: $\hatDelta$  \item \texttt{hatE}: $\hatE$  \item \texttt{hatEE}: $\hatEE$  \item \texttt{hatF}: $\hatF$  \item \texttt{hatFF}: $\hatFF$  \item \texttt{hatG}: $\hatG$  \item \texttt{hatGG}: $\hatGG$  \item \texttt{hatGamma}: $\hatGamma$  \item \texttt{hatH}: $\hatH$  \item \texttt{hatHH}: $\hatHH$  \item \texttt{hatI}: $\hatI$  \item \texttt{hatII}: $\hatII$  \item \texttt{hatJ}: $\hatJ$  \item \texttt{hatJJ}: $\hatJJ$  \item \texttt{hatK}: $\hatK$  \item \texttt{hatKK}: $\hatKK$  \item \texttt{hatL}: $\hatL$  \item \texttt{hatLL}: $\hatLL$  \item \texttt{hatLambda}: $\hatLambda$  \item \texttt{hatM}: $\hatM$  \item \texttt{hatMM}: $\hatMM$  \item \texttt{hatN}: $\hatN$  \item \texttt{hatNN}: $\hatNN$  \item \texttt{hatO}: $\hatO$  \item \texttt{hatOO}: $\hatOO$  \item \texttt{hatOmega}: $\hatOmega$  \item \texttt{hatP}: $\hatP$  \item \texttt{hatPP}: $\hatPP$  \item \texttt{hatPhi}: $\hatPhi$  \item \texttt{hatPi}: $\hatPi$  \item \texttt{hatPsi}: $\hatPsi$  \item \texttt{hatQ}: $\hatQ$  \item \texttt{hatQQ}: $\hatQQ$  \item \texttt{hatR}: $\hatR$  \item \texttt{hatRR}: $\hatRR$  \item \texttt{hatS}: $\hatS$  \item \texttt{hatSS}: $\hatSS$  \item \texttt{hatSigma}: $\hatSigma$  \item \texttt{hatT}: $\hatT$  \item \texttt{hatTT}: $\hatTT$  \item \texttt{hatTheta}: $\hatTheta$  \item \texttt{hatU}: $\hatU$  \item \texttt{hatUU}: $\hatUU$  \item \texttt{hatUpsilon}: $\hatUpsilon$  \item \texttt{hatV}: $\hatV$  \item \texttt{hatVV}: $\hatVV$  \item \texttt{hatW}: $\hatW$  \item \texttt{hatWW}: $\hatWW$  \item \texttt{hatX}: $\hatX$  \item \texttt{hatXX}: $\hatXX$  \item \texttt{hatXi}: $\hatXi$  \item \texttt{hatY}: $\hatY$  \item \texttt{hatYY}: $\hatYY$  \item \texttt{hatZ}: $\hatZ$  \item \texttt{hatZZ}: $\hatZZ$  \item \texttt{hatalpha}: $\hatalpha$  \item \texttt{hatbeta}: $\hatbeta$  \item \texttt{hatchi}: $\hatchi$  \item \texttt{hatdelta}: $\hatdelta$  \item \texttt{hatepsilon}: $\hatepsilon$  \item \texttt{hateta}: $\hateta$  \item \texttt{hatgamma}: $\hatgamma$  \item \texttt{hatiota}: $\hatiota$  \item \texttt{hatkappa}: $\hatkappa$  \item \texttt{hatlambda}: $\hatlambda$  \item \texttt{hatmu}: $\hatmu$  \item \texttt{hatnu}: $\hatnu$  \item \texttt{hatomega}: $\hatomega$  \item \texttt{hatphi}: $\hatphi$  \item \texttt{hatpi}: $\hatpi$  \item \texttt{hatpsi}: $\hatpsi$  \item \texttt{hatrho}: $\hatrho$  \item \texttt{hatsigma}: $\hatsigma$  \item \texttt{hattau}: $\hattau$  \item \texttt{hattheta}: $\hattheta$  \item \texttt{hatupsilon}: $\hatupsilon$  \item \texttt{hatvarepsilon}: $\hatvarepsilon$  \item \texttt{hatvarphi}: $\hatvarphi$  \item \texttt{hatvarpi}: $\hatvarpi$  \item \texttt{hatvarrho}: $\hatvarrho$  \item \texttt{hatvarsigma}: $\hatvarsigma$  \item \texttt{hatvartheta}: $\hatvartheta$  \item \texttt{hatxi}: $\hatxi$  \item \texttt{hatzeta}: $\hatzeta$  \item \texttt{itA}: $\itA$  \item \texttt{itAA}: $\itAA$  \item \texttt{itB}: $\itB$  \item \texttt{itBB}: $\itBB$  \item \texttt{itC}: $\itC$  \item \texttt{itCC}: $\itCC$  \item \texttt{itD}: $\itD$  \item \texttt{itDD}: $\itDD$  \item \texttt{itE}: $\itE$  \item \texttt{itEE}: $\itEE$  \item \texttt{itF}: $\itF$  \item \texttt{itFF}: $\itFF$  \item \texttt{itG}: $\itG$  \item \texttt{itGG}: $\itGG$  \item \texttt{itH}: $\itH$  \item \texttt{itHH}: $\itHH$  \item \texttt{itI}: $\itI$  \item \texttt{itII}: $\itII$  \item \texttt{itJ}: $\itJ$  \item \texttt{itJJ}: $\itJJ$  \item \texttt{itK}: $\itK$  \item \texttt{itKK}: $\itKK$  \item \texttt{itL}: $\itL$  \item \texttt{itLL}: $\itLL$  \item \texttt{itM}: $\itM$  \item \texttt{itMM}: $\itMM$  \item \texttt{itN}: $\itN$  \item \texttt{itNN}: $\itNN$  \item \texttt{itO}: $\itO$  \item \texttt{itOO}: $\itOO$  \item \texttt{itP}: $\itP$  \item \texttt{itPP}: $\itPP$  \item \texttt{itQ}: $\itQ$  \item \texttt{itQQ}: $\itQQ$  \item \texttt{itR}: $\itR$  \item \texttt{itRR}: $\itRR$  \item \texttt{itS}: $\itS$  \item \texttt{itSS}: $\itSS$  \item \texttt{itT}: $\itT$  \item \texttt{itTT}: $\itTT$  \item \texttt{itU}: $\itU$  \item \texttt{itUU}: $\itUU$  \item \texttt{itV}: $\itV$  \item \texttt{itVV}: $\itVV$  \item \texttt{itW}: $\itW$  \item \texttt{itWW}: $\itWW$  \item \texttt{itX}: $\itX$  \item \texttt{itXX}: $\itXX$  \item \texttt{itY}: $\itY$  \item \texttt{itYY}: $\itYY$  \item \texttt{itZ}: $\itZ$  \item \texttt{itZZ}: $\itZZ$  \item \texttt{oA}: $\oA$  \item \texttt{oAA}: $\oAA$  \item \texttt{oB}: $\oB$  \item \texttt{oBB}: $\oBB$  \item \texttt{oC}: $\oC$  \item \texttt{oCC}: $\oCC$  \item \texttt{oD}: $\oD$  \item \texttt{oDD}: $\oDD$  \item \texttt{oDelta}: $\oDelta$  \item \texttt{oE}: $\oE$  \item \texttt{oEE}: $\oEE$  \item \texttt{oF}: $\oF$  \item \texttt{oFF}: $\oFF$  \item \texttt{oG}: $\oG$  \item \texttt{oGG}: $\oGG$  \item \texttt{oGamma}: $\oGamma$  \item \texttt{oH}: $\oH$  \item \texttt{oHH}: $\oHH$  \item \texttt{oI}: $\oI$  \item \texttt{oII}: $\oII$  \item \texttt{oJ}: $\oJ$  \item \texttt{oJJ}: $\oJJ$  \item \texttt{oK}: $\oK$  \item \texttt{oKK}: $\oKK$  \item \texttt{oL}: $\oL$  \item \texttt{oLL}: $\oLL$  \item \texttt{oLambda}: $\oLambda$  \item \texttt{oM}: $\oM$  \item \texttt{oMM}: $\oMM$  \item \texttt{oN}: $\oN$  \item \texttt{oNN}: $\oNN$  \item \texttt{oO}: $\oO$  \item \texttt{oOO}: $\oOO$  \item \texttt{oOmega}: $\oOmega$  \item \texttt{oP}: $\oP$  \item \texttt{oPP}: $\oPP$  \item \texttt{oPhi}: $\oPhi$  \item \texttt{oPi}: $\oPi$  \item \texttt{oPsi}: $\oPsi$  \item \texttt{oQ}: $\oQ$  \item \texttt{oQQ}: $\oQQ$  \item \texttt{oR}: $\oR$  \item \texttt{oRR}: $\oRR$  \item \texttt{oS}: $\oS$  \item \texttt{oSS}: $\oSS$  \item \texttt{oSigma}: $\oSigma$  \item \texttt{oT}: $\oT$  \item \texttt{oTT}: $\oTT$  \item \texttt{oTheta}: $\oTheta$  \item \texttt{oU}: $\oU$  \item \texttt{oUU}: $\oUU$  \item \texttt{oUpsilon}: $\oUpsilon$  \item \texttt{oV}: $\oV$  \item \texttt{oVV}: $\oVV$  \item \texttt{oW}: $\oW$  \item \texttt{oWW}: $\oWW$  \item \texttt{oX}: $\oX$  \item \texttt{oXX}: $\oXX$  \item \texttt{oXi}: $\oXi$  \item \texttt{oY}: $\oY$  \item \texttt{oYY}: $\oYY$  \item \texttt{oZ}: $\oZ$  \item \texttt{oZZ}: $\oZZ$  \item \texttt{oalpha}: $\oalpha$  \item \texttt{obeta}: $\obeta$  \item \texttt{ochi}: $\ochi$  \item \texttt{odelta}: $\odelta$  \item \texttt{oepsilon}: $\oepsilon$  \item \texttt{oeta}: $\oeta$  \item \texttt{ogamma}: $\ogamma$  \item \texttt{oiota}: $\oiota$  \item \texttt{okappa}: $\okappa$  \item \texttt{olambda}: $\olambda$  \item \texttt{omu}: $\omu$  \item \texttt{onu}: $\onu$  \item \texttt{oomega}: $\oomega$  \item \texttt{ophi}: $\ophi$  \item \texttt{opi}: $\opi$  \item \texttt{opsi}: $\opsi$  \item \texttt{orho}: $\orho$  \item \texttt{osigma}: $\osigma$  \item \texttt{otau}: $\otau$  \item \texttt{otheta}: $\otheta$  \item \texttt{oupsilon}: $\oupsilon$  \item \texttt{ovarepsilon}: $\ovarepsilon$  \item \texttt{ovarphi}: $\ovarphi$  \item \texttt{ovarpi}: $\ovarpi$  \item \texttt{ovarrho}: $\ovarrho$  \item \texttt{ovarsigma}: $\ovarsigma$  \item \texttt{ovartheta}: $\ovartheta$  \item \texttt{oxi}: $\oxi$  \item \texttt{ozeta}: $\ozeta$  \item \texttt{rmA}: $\rmA$  \item \texttt{rmAA}: $\rmAA$  \item \texttt{rmB}: $\rmB$  \item \texttt{rmBB}: $\rmBB$  \item \texttt{rmC}: $\rmC$  \item \texttt{rmCC}: $\rmCC$  \item \texttt{rmD}: $\rmD$  \item \texttt{rmDD}: $\rmDD$  \item \texttt{rmE}: $\rmE$  \item \texttt{rmEE}: $\rmEE$  \item \texttt{rmF}: $\rmF$  \item \texttt{rmFF}: $\rmFF$  \item \texttt{rmG}: $\rmG$  \item \texttt{rmGG}: $\rmGG$  \item \texttt{rmH}: $\rmH$  \item \texttt{rmHH}: $\rmHH$  \item \texttt{rmI}: $\rmI$  \item \texttt{rmII}: $\rmII$  \item \texttt{rmJ}: $\rmJ$  \item \texttt{rmJJ}: $\rmJJ$  \item \texttt{rmK}: $\rmK$  \item \texttt{rmKK}: $\rmKK$  \item \texttt{rmL}: $\rmL$  \item \texttt{rmLL}: $\rmLL$  \item \texttt{rmM}: $\rmM$  \item \texttt{rmMM}: $\rmMM$  \item \texttt{rmN}: $\rmN$  \item \texttt{rmNN}: $\rmNN$  \item \texttt{rmO}: $\rmO$  \item \texttt{rmOO}: $\rmOO$  \item \texttt{rmP}: $\rmP$  \item \texttt{rmPP}: $\rmPP$  \item \texttt{rmQ}: $\rmQ$  \item \texttt{rmQQ}: $\rmQQ$  \item \texttt{rmR}: $\rmR$  \item \texttt{rmRR}: $\rmRR$  \item \texttt{rmS}: $\rmS$  \item \texttt{rmSS}: $\rmSS$  \item \texttt{rmT}: $\rmT$  \item \texttt{rmTT}: $\rmTT$  \item \texttt{rmU}: $\rmU$  \item \texttt{rmUU}: $\rmUU$  \item \texttt{rmV}: $\rmV$  \item \texttt{rmVV}: $\rmVV$  \item \texttt{rmW}: $\rmW$  \item \texttt{rmWW}: $\rmWW$  \item \texttt{rmX}: $\rmX$  \item \texttt{rmXX}: $\rmXX$  \item \texttt{rmY}: $\rmY$  \item \texttt{rmYY}: $\rmYY$  \item \texttt{rmZ}: $\rmZ$  \item \texttt{rmZZ}: $\rmZZ$  \item \texttt{sfA}: $\sfA$  \item \texttt{sfAA}: $\sfAA$  \item \texttt{sfB}: $\sfB$  \item \texttt{sfBB}: $\sfBB$  \item \texttt{sfC}: $\sfC$  \item \texttt{sfCC}: $\sfCC$  \item \texttt{sfD}: $\sfD$  \item \texttt{sfDD}: $\sfDD$  \item \texttt{sfE}: $\sfE$  \item \texttt{sfEE}: $\sfEE$  \item \texttt{sfF}: $\sfF$  \item \texttt{sfFF}: $\sfFF$  \item \texttt{sfG}: $\sfG$  \item \texttt{sfGG}: $\sfGG$  \item \texttt{sfH}: $\sfH$  \item \texttt{sfHH}: $\sfHH$  \item \texttt{sfI}: $\sfI$  \item \texttt{sfII}: $\sfII$  \item \texttt{sfJ}: $\sfJ$  \item \texttt{sfJJ}: $\sfJJ$  \item \texttt{sfK}: $\sfK$  \item \texttt{sfKK}: $\sfKK$  \item \texttt{sfL}: $\sfL$  \item \texttt{sfLL}: $\sfLL$  \item \texttt{sfM}: $\sfM$  \item \texttt{sfMM}: $\sfMM$  \item \texttt{sfN}: $\sfN$  \item \texttt{sfNN}: $\sfNN$  \item \texttt{sfO}: $\sfO$  \item \texttt{sfOO}: $\sfOO$  \item \texttt{sfP}: $\sfP$  \item \texttt{sfPP}: $\sfPP$  \item \texttt{sfQ}: $\sfQ$  \item \texttt{sfQQ}: $\sfQQ$  \item \texttt{sfR}: $\sfR$  \item \texttt{sfRR}: $\sfRR$  \item \texttt{sfS}: $\sfS$  \item \texttt{sfSS}: $\sfSS$  \item \texttt{sfT}: $\sfT$  \item \texttt{sfTT}: $\sfTT$  \item \texttt{sfU}: $\sfU$  \item \texttt{sfUU}: $\sfUU$  \item \texttt{sfV}: $\sfV$  \item \texttt{sfVV}: $\sfVV$  \item \texttt{sfW}: $\sfW$  \item \texttt{sfWW}: $\sfWW$  \item \texttt{sfX}: $\sfX$  \item \texttt{sfXX}: $\sfXX$  \item \texttt{sfY}: $\sfY$  \item \texttt{sfYY}: $\sfYY$  \item \texttt{sfZ}: $\sfZ$  \item \texttt{sfZZ}: $\sfZZ$  \item \texttt{tildA}: $\tildA$  \item \texttt{tildAA}: $\tildAA$  \item \texttt{tildB}: $\tildB$  \item \texttt{tildBB}: $\tildBB$  \item \texttt{tildC}: $\tildC$  \item \texttt{tildCC}: $\tildCC$  \item \texttt{tildD}: $\tildD$  \item \texttt{tildDD}: $\tildDD$  \item \texttt{tildDelta}: $\tildDelta$  \item \texttt{tildE}: $\tildE$  \item \texttt{tildEE}: $\tildEE$  \item \texttt{tildF}: $\tildF$  \item \texttt{tildFF}: $\tildFF$  \item \texttt{tildG}: $\tildG$  \item \texttt{tildGG}: $\tildGG$  \item \texttt{tildGamma}: $\tildGamma$  \item \texttt{tildH}: $\tildH$  \item \texttt{tildHH}: $\tildHH$  \item \texttt{tildI}: $\tildI$  \item \texttt{tildII}: $\tildII$  \item \texttt{tildJ}: $\tildJ$  \item \texttt{tildJJ}: $\tildJJ$  \item \texttt{tildK}: $\tildK$  \item \texttt{tildKK}: $\tildKK$  \item \texttt{tildL}: $\tildL$  \item \texttt{tildLL}: $\tildLL$  \item \texttt{tildLambda}: $\tildLambda$  \item \texttt{tildM}: $\tildM$  \item \texttt{tildMM}: $\tildMM$  \item \texttt{tildN}: $\tildN$  \item \texttt{tildNN}: $\tildNN$  \item \texttt{tildO}: $\tildO$  \item \texttt{tildOO}: $\tildOO$  \item \texttt{tildOmega}: $\tildOmega$  \item \texttt{tildP}: $\tildP$  \item \texttt{tildPP}: $\tildPP$  \item \texttt{tildPhi}: $\tildPhi$  \item \texttt{tildPi}: $\tildPi$  \item \texttt{tildPsi}: $\tildPsi$  \item \texttt{tildQ}: $\tildQ$  \item \texttt{tildQQ}: $\tildQQ$  \item \texttt{tildR}: $\tildR$  \item \texttt{tildRR}: $\tildRR$  \item \texttt{tildS}: $\tildS$  \item \texttt{tildSS}: $\tildSS$  \item \texttt{tildSigma}: $\tildSigma$  \item \texttt{tildT}: $\tildT$  \item \texttt{tildTT}: $\tildTT$  \item \texttt{tildTheta}: $\tildTheta$  \item \texttt{tildU}: $\tildU$  \item \texttt{tildUU}: $\tildUU$  \item \texttt{tildUpsilon}: $\tildUpsilon$  \item \texttt{tildV}: $\tildV$  \item \texttt{tildVV}: $\tildVV$  \item \texttt{tildW}: $\tildW$  \item \texttt{tildWW}: $\tildWW$  \item \texttt{tildX}: $\tildX$  \item \texttt{tildXX}: $\tildXX$  \item \texttt{tildXi}: $\tildXi$  \item \texttt{tildY}: $\tildY$  \item \texttt{tildYY}: $\tildYY$  \item \texttt{tildZ}: $\tildZ$  \item \texttt{tildZZ}: $\tildZZ$  \item \texttt{tildalpha}: $\tildalpha$  \item \texttt{tildbeta}: $\tildbeta$  \item \texttt{tildchi}: $\tildchi$  \item \texttt{tilddelta}: $\tilddelta$  \item \texttt{tildepsilon}: $\tildepsilon$  \item \texttt{tildeta}: $\tildeta$  \item \texttt{tildgamma}: $\tildgamma$  \item \texttt{tildiota}: $\tildiota$  \item \texttt{tildkappa}: $\tildkappa$  \item \texttt{tildlambda}: $\tildlambda$  \item \texttt{tildmu}: $\tildmu$  \item \texttt{tildnu}: $\tildnu$  \item \texttt{tildomega}: $\tildomega$  \item \texttt{tildphi}: $\tildphi$  \item \texttt{tildpi}: $\tildpi$  \item \texttt{tildpsi}: $\tildpsi$  \item \texttt{tildrho}: $\tildrho$  \item \texttt{tildsigma}: $\tildsigma$  \item \texttt{tildtau}: $\tildtau$  \item \texttt{tildtheta}: $\tildtheta$  \item \texttt{tildupsilon}: $\tildupsilon$  \item \texttt{tildvarepsilon}: $\tildvarepsilon$  \item \texttt{tildvarphi}: $\tildvarphi$  \item \texttt{tildvarpi}: $\tildvarpi$  \item \texttt{tildvarrho}: $\tildvarrho$  \item \texttt{tildvarsigma}: $\tildvarsigma$  \item \texttt{tildvartheta}: $\tildvartheta$  \item \texttt{tildxi}: $\tildxi$  \item \texttt{tildzeta}: $\tildzeta$  \item \texttt{uA}: $\uA$  \item \texttt{uAA}: $\uAA$  \item \texttt{uB}: $\uB$  \item \texttt{uBB}: $\uBB$  \item \texttt{uC}: $\uC$  \item \texttt{uCC}: $\uCC$  \item \texttt{uD}: $\uD$  \item \texttt{uDD}: $\uDD$  \item \texttt{uDelta}: $\uDelta$  \item \texttt{uE}: $\uE$  \item \texttt{uEE}: $\uEE$  \item \texttt{uF}: $\uF$  \item \texttt{uFF}: $\uFF$  \item \texttt{uG}: $\uG$  \item \texttt{uGG}: $\uGG$  \item \texttt{uGamma}: $\uGamma$  \item \texttt{uH}: $\uH$  \item \texttt{uHH}: $\uHH$  \item \texttt{uI}: $\uI$  \item \texttt{uII}: $\uII$  \item \texttt{uJ}: $\uJ$  \item \texttt{uJJ}: $\uJJ$  \item \texttt{uK}: $\uK$  \item \texttt{uKK}: $\uKK$  \item \texttt{uL}: $\uL$  \item \texttt{uLL}: $\uLL$  \item \texttt{uLambda}: $\uLambda$  \item \texttt{uM}: $\uM$  \item \texttt{uMM}: $\uMM$  \item \texttt{uN}: $\uN$  \item \texttt{uNN}: $\uNN$  \item \texttt{uO}: $\uO$  \item \texttt{uOO}: $\uOO$  \item \texttt{uOmega}: $\uOmega$  \item \texttt{uP}: $\uP$  \item \texttt{uPP}: $\uPP$  \item \texttt{uPhi}: $\uPhi$  \item \texttt{uPi}: $\uPi$  \item \texttt{uPsi}: $\uPsi$  \item \texttt{uQ}: $\uQ$  \item \texttt{uQQ}: $\uQQ$  \item \texttt{uR}: $\uR$  \item \texttt{uRR}: $\uRR$  \item \texttt{uS}: $\uS$  \item \texttt{uSS}: $\uSS$  \item \texttt{uSigma}: $\uSigma$  \item \texttt{uT}: $\uT$  \item \texttt{uTT}: $\uTT$  \item \texttt{uTheta}: $\uTheta$  \item \texttt{uU}: $\uU$  \item \texttt{uUU}: $\uUU$  \item \texttt{uUpsilon}: $\uUpsilon$  \item \texttt{uV}: $\uV$  \item \texttt{uVV}: $\uVV$  \item \texttt{uW}: $\uW$  \item \texttt{uWW}: $\uWW$  \item \texttt{uX}: $\uX$  \item \texttt{uXX}: $\uXX$  \item \texttt{uXi}: $\uXi$  \item \texttt{uY}: $\uY$  \item \texttt{uYY}: $\uYY$  \item \texttt{uZ}: $\uZ$  \item \texttt{uZZ}: $\uZZ$  \item \texttt{ualpha}: $\ualpha$  \item \texttt{ubeta}: $\ubeta$  \item \texttt{uchi}: $\uchi$  \item \texttt{udelta}: $\udelta$  \item \texttt{uepsilon}: $\uepsilon$  \item \texttt{ueta}: $\ueta$  \item \texttt{ugamma}: $\ugamma$  \item \texttt{uiota}: $\uiota$  \item \texttt{ukappa}: $\ukappa$  \item \texttt{ulambda}: $\ulambda$  \item \texttt{umu}: $\umu$  \item \texttt{unu}: $\unu$  \item \texttt{uomega}: $\uomega$  \item \texttt{uphi}: $\uphi$  \item \texttt{upi}: $\upi$  \item \texttt{upsi}: $\upsi$  \item \texttt{urho}: $\urho$  \item \texttt{usigma}: $\usigma$  \item \texttt{utau}: $\utau$  \item \texttt{utheta}: $\utheta$  \item \texttt{uuA}: $\uuA$  \item \texttt{uuAA}: $\uuAA$  \item \texttt{uuB}: $\uuB$  \item \texttt{uuBB}: $\uuBB$  \item \texttt{uuC}: $\uuC$  \item \texttt{uuCC}: $\uuCC$  \item \texttt{uuD}: $\uuD$  \item \texttt{uuDD}: $\uuDD$  \item \texttt{uuDelta}: $\uuDelta$  \item \texttt{uuE}: $\uuE$  \item \texttt{uuEE}: $\uuEE$  \item \texttt{uuF}: $\uuF$  \item \texttt{uuFF}: $\uuFF$  \item \texttt{uuG}: $\uuG$  \item \texttt{uuGG}: $\uuGG$  \item \texttt{uuGamma}: $\uuGamma$  \item \texttt{uuH}: $\uuH$  \item \texttt{uuHH}: $\uuHH$  \item \texttt{uuI}: $\uuI$  \item \texttt{uuII}: $\uuII$  \item \texttt{uuJ}: $\uuJ$  \item \texttt{uuJJ}: $\uuJJ$  \item \texttt{uuK}: $\uuK$  \item \texttt{uuKK}: $\uuKK$  \item \texttt{uuL}: $\uuL$  \item \texttt{uuLL}: $\uuLL$  \item \texttt{uuLambda}: $\uuLambda$  \item \texttt{uuM}: $\uuM$  \item \texttt{uuMM}: $\uuMM$  \item \texttt{uuN}: $\uuN$  \item \texttt{uuNN}: $\uuNN$  \item \texttt{uuO}: $\uuO$  \item \texttt{uuOO}: $\uuOO$  \item \texttt{uuOmega}: $\uuOmega$  \item \texttt{uuP}: $\uuP$  \item \texttt{uuPP}: $\uuPP$  \item \texttt{uuPhi}: $\uuPhi$  \item \texttt{uuPi}: $\uuPi$  \item \texttt{uuPsi}: $\uuPsi$  \item \texttt{uuQ}: $\uuQ$  \item \texttt{uuQQ}: $\uuQQ$  \item \texttt{uuR}: $\uuR$  \item \texttt{uuRR}: $\uuRR$  \item \texttt{uuS}: $\uuS$  \item \texttt{uuSS}: $\uuSS$  \item \texttt{uuSigma}: $\uuSigma$  \item \texttt{uuT}: $\uuT$  \item \texttt{uuTT}: $\uuTT$  \item \texttt{uuTheta}: $\uuTheta$  \item \texttt{uuU}: $\uuU$  \item \texttt{uuUU}: $\uuUU$  \item \texttt{uuUpsilon}: $\uuUpsilon$  \item \texttt{uuV}: $\uuV$  \item \texttt{uuVV}: $\uuVV$  \item \texttt{uuW}: $\uuW$  \item \texttt{uuWW}: $\uuWW$  \item \texttt{uuX}: $\uuX$  \item \texttt{uuXX}: $\uuXX$  \item \texttt{uuXi}: $\uuXi$  \item \texttt{uuY}: $\uuY$  \item \texttt{uuYY}: $\uuYY$  \item \texttt{uuZ}: $\uuZ$  \item \texttt{uuZZ}: $\uuZZ$  \item \texttt{uualpha}: $\uualpha$  \item \texttt{uubeta}: $\uubeta$  \item \texttt{uuchi}: $\uuchi$  \item \texttt{uudelta}: $\uudelta$  \item \texttt{uuepsilon}: $\uuepsilon$  \item \texttt{uueta}: $\uueta$  \item \texttt{uugamma}: $\uugamma$  \item \texttt{uuiota}: $\uuiota$  \item \texttt{uukappa}: $\uukappa$  \item \texttt{uulambda}: $\uulambda$  \item \texttt{uumu}: $\uumu$  \item \texttt{uunu}: $\uunu$  \item \texttt{uuomega}: $\uuomega$  \item \texttt{uuphi}: $\uuphi$  \item \texttt{uupi}: $\uupi$  \item \texttt{uupsi}: $\uupsi$  \item \texttt{uupsilon}: $\uupsilon$  \item \texttt{uurho}: $\uurho$  \item \texttt{uusigma}: $\uusigma$  \item \texttt{uutau}: $\uutau$  \item \texttt{uutheta}: $\uutheta$  \item \texttt{uuupsilon}: $\uuupsilon$  \item \texttt{uuvarepsilon}: $\uuvarepsilon$  \item \texttt{uuvarphi}: $\uuvarphi$  \item \texttt{uuvarpi}: $\uuvarpi$  \item \texttt{uuvarrho}: $\uuvarrho$  \item \texttt{uuvarsigma}: $\uuvarsigma$  \item \texttt{uuvartheta}: $\uuvartheta$  \item \texttt{uuxi}: $\uuxi$  \item \texttt{uuzeta}: $\uuzeta$  \item \texttt{uvarepsilon}: $\uvarepsilon$  \item \texttt{uvarphi}: $\uvarphi$  \item \texttt{uvarpi}: $\uvarpi$  \item \texttt{uvarrho}: $\uvarrho$  \item \texttt{uvarsigma}: $\uvarsigma$  \item \texttt{uvartheta}: $\uvartheta$  \item \texttt{uxi}: $\uxi$  \item \texttt{uzeta}: $\uzeta$  \item \texttt{vecA}: $\vecA$  \item \texttt{vecAA}: $\vecAA$  \item \texttt{vecB}: $\vecB$  \item \texttt{vecBB}: $\vecBB$  \item \texttt{vecC}: $\vecC$  \item \texttt{vecCC}: $\vecCC$  \item \texttt{vecD}: $\vecD$  \item \texttt{vecDD}: $\vecDD$  \item \texttt{vecDelta}: $\vecDelta$  \item \texttt{vecE}: $\vecE$  \item \texttt{vecEE}: $\vecEE$  \item \texttt{vecF}: $\vecF$  \item \texttt{vecFF}: $\vecFF$  \item \texttt{vecG}: $\vecG$  \item \texttt{vecGG}: $\vecGG$  \item \texttt{vecGamma}: $\vecGamma$  \item \texttt{vecH}: $\vecH$  \item \texttt{vecHH}: $\vecHH$  \item \texttt{vecI}: $\vecI$  \item \texttt{vecII}: $\vecII$  \item \texttt{vecJ}: $\vecJ$  \item \texttt{vecJJ}: $\vecJJ$  \item \texttt{vecK}: $\vecK$  \item \texttt{vecKK}: $\vecKK$  \item \texttt{vecL}: $\vecL$  \item \texttt{vecLL}: $\vecLL$  \item \texttt{vecLambda}: $\vecLambda$  \item \texttt{vecM}: $\vecM$  \item \texttt{vecMM}: $\vecMM$  \item \texttt{vecN}: $\vecN$  \item \texttt{vecNN}: $\vecNN$  \item \texttt{vecO}: $\vecO$  \item \texttt{vecOO}: $\vecOO$  \item \texttt{vecOmega}: $\vecOmega$  \item \texttt{vecP}: $\vecP$  \item \texttt{vecPP}: $\vecPP$  \item \texttt{vecPhi}: $\vecPhi$  \item \texttt{vecPi}: $\vecPi$  \item \texttt{vecPsi}: $\vecPsi$  \item \texttt{vecQ}: $\vecQ$  \item \texttt{vecQQ}: $\vecQQ$  \item \texttt{vecR}: $\vecR$  \item \texttt{vecRR}: $\vecRR$  \item \texttt{vecS}: $\vecS$  \item \texttt{vecSS}: $\vecSS$  \item \texttt{vecSigma}: $\vecSigma$  \item \texttt{vecT}: $\vecT$  \item \texttt{vecTT}: $\vecTT$  \item \texttt{vecTheta}: $\vecTheta$  \item \texttt{vecU}: $\vecU$  \item \texttt{vecUU}: $\vecUU$  \item \texttt{vecUpsilon}: $\vecUpsilon$  \item \texttt{vecV}: $\vecV$  \item \texttt{vecVV}: $\vecVV$  \item \texttt{vecW}: $\vecW$  \item \texttt{vecWW}: $\vecWW$  \item \texttt{vecX}: $\vecX$  \item \texttt{vecXX}: $\vecXX$  \item \texttt{vecXi}: $\vecXi$  \item \texttt{vecY}: $\vecY$  \item \texttt{vecYY}: $\vecYY$  \item \texttt{vecZ}: $\vecZ$  \item \texttt{vecZZ}: $\vecZZ$  \item \texttt{vecalpha}: $\vecalpha$  \item \texttt{vecbeta}: $\vecbeta$  \item \texttt{vecchi}: $\vecchi$  \item \texttt{vecdelta}: $\vecdelta$  \item \texttt{vecepsilon}: $\vecepsilon$  \item \texttt{veceta}: $\veceta$  \item \texttt{vecgamma}: $\vecgamma$  \item \texttt{veciota}: $\veciota$  \item \texttt{veckappa}: $\veckappa$  \item \texttt{veclambda}: $\veclambda$  \item \texttt{vecmu}: $\vecmu$  \item \texttt{vecnu}: $\vecnu$  \item \texttt{vecomega}: $\vecomega$  \item \texttt{vecphi}: $\vecphi$  \item \texttt{vecpi}: $\vecpi$  \item \texttt{vecpsi}: $\vecpsi$  \item \texttt{vecrho}: $\vecrho$  \item \texttt{vecsigma}: $\vecsigma$  \item \texttt{vectau}: $\vectau$  \item \texttt{vectheta}: $\vectheta$  \item \texttt{vecupsilon}: $\vecupsilon$  \item \texttt{vecvarepsilon}: $\vecvarepsilon$  \item \texttt{vecvarphi}: $\vecvarphi$  \item \texttt{vecvarpi}: $\vecvarpi$  \item \texttt{vecvarrho}: $\vecvarrho$  \item \texttt{vecvarsigma}: $\vecvarsigma$  \item \texttt{vecvartheta}: $\vecvartheta$  \item \texttt{vecxi}: $\vecxi$  \item \texttt{veczeta}: $\veczeta$\end{enumerate}\end{multicols}\section{Internal commands}\begin{multicols}{3}\begin{enumerate}  \item \texttt{\@b\_core\_use\_autoPackInclusion}: Wether \texttt{kappak} should automatically include core packages or not.  \item \texttt{\@b\_extpack\_auto}: Wether \texttt{kappak} should automatically include non core packages or not.  \item \texttt{\@b\_extpack\_tikz\_externalize}: Wether \texttt{kappak} should set the  \texttt{tikz} compilation cache or not. (doesn't work)  \item \texttt{\@b\_extpack\_use\_stix}: Wether \texttt{kappak} should use \texttt{stix} or not.  \item \texttt{\@b\_extpack\_use\_tikz}: Wether \texttt{kappak} should use \texttt{tikz} or not.  \item \texttt{\@b\_extpack\_use\_xecjk}: Wether \texttt{kappak} should use \texttt{xecjk} or not.  \item \texttt{\@b\_maths\_use\_arrows}:   \item \texttt{\@b\_maths\_use\_categories}:   \item \texttt{\@b\_maths\_use\_characterAccents}:   \item \texttt{\@b\_maths\_use\_characterStyles}:   \item \texttt{\@b\_maths\_use\_misc}:   \item \texttt{\@b\_maths\_use\_operators}:   \item \texttt{\@b\_maths\_use\_theoremEnvs}:   \item \texttt{\@b\_maths\_use\_theoremStyles}:   \item \texttt{\@b\_use\_misc}:   \item \texttt{\@bbStyle}:   \item \texttt{\@bbStyle}:   \item \texttt{\@bibliographyStyle}:   \item \texttt{\@bibliographyStyle}:   \item \texttt{\@categoryStyle}:   \item \texttt{\@categoryStyle}:    \item \texttt{\@chapterStyle}:   \item \texttt{\@chapterStyle}:   \item \texttt{\@fontSet}:   \item \texttt{\@fontSet}:   \item \texttt{\@headerFooterStyle}:   \item \texttt{\@headerFooterStyle}:   \item \texttt{\@language}:   \item \texttt{\@language}:   \item \texttt{\@margins}:   \item \texttt{\@margins}:   \item \texttt{\@scriptStyle}:   \item \texttt{\@scriptStyle}:   \item \texttt{\@titlePageStyle}:   \item \texttt{\@titlePageStyle}: \end{enumerate}\end{multicols}\end{document}